The ChEMBL database as Linked Open Data

### 2013-01-22 article.tex
Directly linked BAO to the need of an 'activity type' ontology
Removed the repetitive, almost identical SPARQL queries

It should also be noted that all drug-like entities in ChEMBL are not ontologically
subclassing a drug class. Instead, we give the entities the role of drug: only within a
particular context, they would be drug. If not used as medication, they are not drug.
Moreover, the triples only attach this drug role to approved drugs, as defined by the
ChEMBL database. All drug-like entities in the database do not have the role of drug.
The role is triplified using the OBO and ChEBI ontologies in the following manner,
where CHEBI\_23888 is the ontological entry for ``drug role'' in ChEBI:

@@

The ongoing ChEMBL-RDF project is Open Source making it possible to others to convert ChEMBL to RDF too.
The ChEMBL team (JO, AG, MD) plans to be a primary source of a RDF version of ChEMBL, while others continue
exposing ChEMBL as RDF (EW, PA). Different versions may arise which expose the data using different ontologies,
supporting current community needs, however, convergence is expected after a period of experimenting with ontologies that
may not prove to be practically useful. The availability of Open Source scripts ensures that the community can contribute to the
process of choosing a practically useful set of ontological terms.

>>>>

It should also be noted that all drug-like entities in ChEMBL are not ontologically
subclassing a drug class. Instead, we give the entities the role of drug: only within a
particular context, they would be drug. If not used as medication, they are not drug.
Moreover, the triples only attach this drug role to approved drugs, as defined by the
ChEMBL database. All drug-like entities in the database do not have the role of drug.
The role is triplified using the OBO and ChEBI ontologies in the following manner,
where CHEBI\_23888 is the ontological entry for of ``drug role'' in ChEBI:

@@

The ongoing ChEMBL-RDF project is Open Source making it possible to others to convert ChEMBL to RDF too.
The ChEMBL team (JO, AG, MD) plans to be a primary source of a RDF version of ChEMBL, while others continue
exposing ChEMBL as RDF too (EW, PA). Various version may arise, exposing the data in different ontologies,
supporting community needs, though convergence may arise after a period of experimenting with ontologies that
will not survive the test of time. The availability of Open Source scripts ensure an easy switch from one
ontology to another.
